\newpage
\large{Be sure to see \url{https://www.sciencemag.org/node/2385628}
  for info on
  Sci. Robotics Perspectives and what they're looking for}\\


Potential folks to recruit, once we have a baseline draft; those in
\ic{red} are likely to contribute text:

\begin{enumerate}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
\footnotesize{  
\item \ic{Jo Eidsvik} (NO) NTNU, Trondheim -— Statistics and Sampling https://www.ntnu.edu/employees/jo.eidsvik
\item \ic{Rick Stumpf} (US) NOAA — coastal oceanography -- https://www.gulfbase.org/people/dr-richard-p-stumpf
\item Catarina Magalhaes (PO) Univ. of Porto, CIIMAR — biological oceanography -- https://www2.ciimar.up.pt/team.php?id=85
\item Stef Williams (AUS) Univ. of Sydney — Marine Robotics -- https://www.sydney.edu.au/engineering/about/our-people/academic-staff/stefan-williams.html
\item \ic{Ralf Bachmeyer} (DE) Univ. of Bremen, Germany — Marine Robotics -- https://www.marum.de/en/Prof.-Dr.-ralf-bachmayer.html
\item \ic{Yogi Girdhar} (US), WHOI — Marine Robotics and ML -- https://www.whoi.edu/profile/ygirdhar/
\item Paulo Relvas (PO), Univ. of Algarve, Portugal — Phys. Oceanography -- https://www.ccmar.ualg.pt/users/prelvas
\item Marta Chantal Ribeiro (PO) Univ. of Porto, CIIMAR -— Maritime Law and MPA’s -— https://www2.ciimar.up.pt/team.php?id=279
\item Oliver Zelinskly (DE), Oldenberg, Germany -- Sensors and ML -- https://uol.de/en/icbm/marine-sensor-systems
\item Nadia Pinardi (IT) Bologna, Italy -- Phys. Oceanography -- https://www.unibo.it/sitoweb/nadia.pinardi/en
\item \ic{Oscar Scholfield} (US) Rutgers -- biological oceanographer -- https://marine.rutgers.edu/team/oscar-schofield/  
\item Mark Moline (US) Univ. of Delaware -- biological oceanographer -- https://www.udel.edu/academics/colleges/ceoe/departments/smsp/faculty/mark-moline/
\item Pere Ridao (ES) Univ. of Girona -- Marine Robotics -- http://eia.udg.es/~pere/Pere\_Ridao\_Home\_Page/Short\_CV.html
\item Mandar Chitre (SG) National Univ. Singapore -- Marine Robotics
  and acoustics -- http://www.chitre.net/

}
\end{enumerate}
